Information Disclosure in Dynamic Innovation Contests

### 2025-07-14 paper/Paper.tex
update

@@

An additional assumption underlying the data-generating process pertains to the assumption that leaderboard data follow a normal distribution.

@@

%%%%%%%%%% Figure & Table %%%%%%%%%%%
\noindent
\begin{minipage}[t]{0.43\textwidth}
	\vspace*{\fill}
	\centering
	\includegraphics[width=\linewidth]{validate_lamb.pdf}
	\vspace*{\fill}
\end{minipage}
\hfill
\begin{minipage}[t]{0.53\textwidth}
	\vspace*{\fill}
	\centering
	\newcolumntype{Y}{>{\centering\arraybackslash}X}
	\begin{tabularx}{\textwidth}{llYY}
		\toprule
		& coef. & stderr & 95\% CI \\
		\midrule
		const.
		& -0.8.30 & 3.122 & [-7.051, 5.392] \\
		$\log(1 + \hat{\lambda})$ 
		& 3.288\textbf{**} & 1.067 & [1.161, 5.416] \\
		\midrule
		Obs. & \multicolumn{3}{c}{75} \\
		R$^2$ & \multicolumn{3}{c}{0.115} \\
		Adj. R$^2$ & \multicolumn{3}{c}{0.103} \\
		\bottomrule
		\addlinespace[0.5ex]
	\end{tabularx}
	\begin{minipage}{\textwidth}
{\footnotesize
\textit{Note:} (1) Significance levels: \textbf{***} $p < 0.001$, \textbf{**} $p < 0.01$, \textbf{*} $p < 0.05$. 
(2) Normality diagnostics: Omnibus = 0.449, Jarque-Bera = 0.091, Skewness = 0.016, Kurtosis = 3.168. 
(3) Other diagnostic statistics: Condition Number = 28.2, Durbin-Watson = 2.212.
}
	\end{minipage}
	\vspace*{\fill}
\end{minipage}
%%%%%%%%%%%% Captions %%%%%%%%%%%%
\noindent
\begin{minipage}[t]{\textwidth}
	\centering
	\captionof{figure}{$\lambda^{\text{MLE}}$ vs. Bayesian Estimate $\hat\lambda$}
	\label{fig-validate-lambda}
\end{minipage}
%\hfill
%\begin{minipage}[t]{0.53\textwidth}
%	\centering
%	\captionof{table}{Regression of $\lambda^{\text{MLE}}$ on Bayesian Estimate $\hat\lambda$}
%\end{minipage}
\medskip

@@

>>>>

\subsubsection{Two Players.}

An additional concern underlying the data-generating process pertains to the assumption that there are only two contestants participating in the entire competition.
The implication of this assumption in the context of crowdsourcing platforms like Kaggle is that each team has a clear understanding of the capabilities of all other competitors, allowing the two strongest teams to mutually recognize each other. 
In reality, however, this assumption considerably oversimplifies the problem.
In Section~\ref{sect-robust-2players}, we conduct a series of robustness checks. 
By selecting the top two competitors using alternative criteria, we aim to assess whether the earlier conclusions remain valid.

@@

Another aspect of the data-generating assumptions that may be open to question is the assumption of normality. 
Specifically, we rely on normal distributions in two critical components: the signal noise and the innovation shock. 
As discussed in Section~\ref{sec-data-clean}, maintaining this assumption depends heavily on our data transformation procedures, such as converting percentage leaderboard data into the state variable $\hat{y}_t$. 
When applying a uniform transformation across all contests, we find that for many contests, approximately half, the resulting data do not conform well to a normal distribution. 
This discrepancy has important implications for the credibility of our statistical results.
In Section~\ref{sect-robust-normality}, we adopt alternative data processing methods to assess the robustness of our results.

@@

%%%%%%%%%% Figure & Table %%%%%%%%%%%
\noindent
\begin{minipage}[t]{0.43\textwidth}
	\vspace*{\fill}
	\centering
	\includegraphics[width=\linewidth]{validate_lamb.pdf}
	\vspace*{\fill}
\end{minipage}
\hfill
\begin{minipage}[t]{0.53\textwidth}
	\vspace*{\fill}
	\centering
	\newcolumntype{Y}{>{\centering\arraybackslash}X}
	\begin{tabularx}{\textwidth}{llYY}
		\toprule
		& coef. & stderr & 95\% CI \\
		\midrule
		const.
		& -0.830 & 3.122 & [-7.051, 5.392] \\
		$\log(1 + \hat{\lambda})$ 
		& 3.288\textbf{**} & 1.067 & [1.161, 5.416] \\
		\midrule
		Obs. & \multicolumn{3}{c}{75} \\
		R$^2$ & \multicolumn{3}{c}{0.115} \\
		Adj. R$^2$ & \multicolumn{3}{c}{0.103} \\
		\bottomrule
		\addlinespace[0.5ex]
	\end{tabularx}
	\begin{minipage}{\textwidth}
{\footnotesize
\textit{Note:} (1) Significance levels: \textbf{***} $p < 0.001$, \textbf{**} $p < 0.01$, \textbf{*} $p < 0.05$. 
(2) Normality diagnostics: Omnibus = 0.449, Jarque-Bera = 0.091, Skewness = 0.016, Kurtosis = 3.168. 
(3) Other diagnostic statistics: Condition Number = 28.2, Durbin-Watson = 2.212.
}
	\end{minipage}
	\vspace*{\fill}
\end{minipage}
%%%%%%%%%%%% Captions %%%%%%%%%%%%
\noindent
\begin{minipage}[t]{\textwidth}
	\centering
	\captionof{figure}{$\lambda^{\text{MLE}}$ vs. Bayesian Estimate $\hat\lambda$}
	\label{fig-validate-lambda}
\end{minipage}
%\hfill
%\begin{minipage}[t]{0.53\textwidth}
%	\centering
%	\captionof{table}{Regression of $\lambda^{\text{MLE}}$ on Bayesian Estimate $\hat\lambda$}
%\end{minipage}
\medskip

@@

\section{Robustness}

...

\subsection{}\label{sect-robust-2players}

So far, we ...

Another plausible conjecture is that each contestant perceives themselves as competing against an imagined strongest opponent. 
This perceived benchmark is likely shaped by the public leaderboard performances of several genuinely strong teams, while also being influenced by the top-ranked submission, which often exhibits substantial overfitting to the public leaderboard.

\subsection{}\label{sect-robust-normality}

...
